DOpElib:\\ Differential Equations and Optimization Environment

### 2017-04-12 Examples/Documentation/introduction.tex
optproblemcontainer modified to fit with deal.II 8.5.0

%
\item Get a copy of \texttt{DOpElib}, see Section~\ref{sec:obtain} for details.
%
\item Unpack in your preferred directory:
\begin{lstlisting}
~/Software/> tar -xzf dopelib-4.0.tar.gz
\end{lstlisting}
to get
\begin{lstlisting}
~/Software/dopelib-4.0
\end{lstlisting}
To build the \texttt{DOpElib} you have to change to the directory 
\texttt{DOpEsrc} where you can call 
\begin{lstlisting}
~/Software/dopelib-4.0/DOpEsrc> make c-all
\end{lstlisting}
to build and configure the library using cmake. 
You also get various installation options by just typing 
\texttt{make}.
\item To generate documentation, please go into:
\begin{lstlisting}
~/Software/dopelib-4.0/Examples
\end{lstlisting}
Here, you get all options by typing:
\begin{lstlisting}
make
\end{lstlisting}
Specifically, you can create and run all examples, running a test suite,
and generating documentation:
{\footnotesize
\begin{lstlisting}
===========================================================================
=              Makefile for the DOpE documentation                        =
===========================================================================
=                                                                         =
= The following targets exist:                                            =
=    c-all     :  Make all examples using cmake                           =
=    clean     :  Cleaning up all examples                                =
=    tests     :  Run all test param data.                                =
=    c-cat     :  Run clean, run c-all, run tests (combine these commands)=
=    doc       :  Create documentation in pdf file format via latexmk     =
=    distclean :  Cleaning up, including documentation                    =
=    warncheck :  Checks whether all Examples compile without warnings    =
===========================================================================
\end{lstlisting}
}
The options are $c-all$ and $c-cat$ utilizing the cmake build system.
For html documentation, change into:
\begin{lstlisting}
~/Software/dopelib-4.0/doxygen
\end{lstlisting}
and then typing \texttt{make}. Doxygen documentation
will require either 
latex or doxygen to be installed on your computer.
\item If you wish to test if everything worked. To do so you can 
change to the \texttt{Examples} directory and \texttt{make tests} which will give you a 
list of all the examples and whether they behave as expected by the library, see also 
Chapter~\ref{chap:test}.
\item  If you want to use some of the supported third party libraries install them and follow 
 the instructions in \texttt{ThirdPartyLibs/README}. There may be further information 
 in some \texttt{ThirdPartyLibs/*.INSTALLNOTES} that you may want to
 consider.\\[3mm]
 As example, the installation of ipopt works as follows:\\
In the path \texttt{~/dope/ThirdPartyLibs>} type in the terminal\\
\texttt{./install-free-libs.sh}

@@

This means that the Makefile in the specific examples folder has been 
modified in some illegal way. Remove this Makefile and get the original 
one from DOpElib. Then try again make c-all (make always sure that before 
typing make c-all that the deal.II path is exported - see above).

>>>>

%
\item Get a copy of \texttt{DOpElib}, see Section~\ref{sec:obtain} for details.
%
\item Unpack in your preferred directory:
\begin{lstlisting}
~/Software/> tar -xzf dopelib-4.0.tar.gz
\end{lstlisting}
to get
\begin{lstlisting}
~/Software/dopelib-4.0
\end{lstlisting}
To build the \texttt{DOpElib} you have to change to the directory 
\texttt{DOpEsrc} where you can call 
\begin{lstlisting}
~/Software/dopelib-4.0/DOpEsrc> make c-all
\end{lstlisting}
to build and configure the library using cmake. 
You also get various installation options by just typing 
\texttt{make}.
\item To generate documentation, please go into:
\begin{lstlisting}
~/Software/dopelib-4.0/Examples
\end{lstlisting}
Here, you get all options by typing:
\begin{lstlisting}
make
\end{lstlisting}
Specifically, you can create and run all examples, running a test suite,
and generating documentation:
{\footnotesize
\begin{lstlisting}
===========================================================================
=              Makefile for the DOpE documentation                        =
===========================================================================
=                                                                         =
= The following targets exist:                                            =
=    c-all     :  Make all examples using cmake                           =
=    clean     :  Cleaning up all examples                                =
=    tests     :  Run all test param data.                                =
=    c-cat     :  Run clean, run c-all, run tests (combine these commands)=
=    doc       :  Create documentation in pdf file format via latexmk     =
=    distclean :  Cleaning up, including documentation                    =
=    warncheck :  Checks whether all Examples compile without warnings    =
===========================================================================
\end{lstlisting}
}
The options are $c-all$ and $c-cat$ utilizing the cmake build system.

It is \textbf{important} to generate the examples via make c-all 
in the home folder of the examples and \textbf{not} as in deal.II by 
using cmake . in the specific example itself. With this you
would currently destroy the delivered Makefile. See also the FAQ below.

For html documentation, change into:
\begin{lstlisting}
~/Software/dopelib-4.0/doxygen
\end{lstlisting}
and then typing \texttt{make}. Doxygen documentation
will require either 
latex or doxygen to be installed on your computer.
\item If you wish to test if everything worked. To do so you can 
change to the \texttt{Examples} directory and \texttt{make tests} which will give you a 
list of all the examples and whether they behave as expected by the library, see also 
Chapter~\ref{chap:test}.
\item  If you want to use some of the supported third party libraries install them and follow 
 the instructions in \texttt{ThirdPartyLibs/README}. There may be further information 
 in some \texttt{ThirdPartyLibs/*.INSTALLNOTES} that you may want to
 consider.\\[3mm]
 As example, the installation of ipopt works as follows:\\
In the path \texttt{~/dope/ThirdPartyLibs>} type in the terminal\\
\texttt{./install-free-libs.sh}

@@

This means that the Makefile in the specific examples folder has been 
modified in some illegal way. Remove this Makefile 
\begin{lstlisting}
rm Makefile
rm -r CMakeFiles
rm CMakeCache.txt
rm -r autobuild
\end{lstlisting}
and get the original 
one from DOpElib:
\begin{lstlisting}
git checkout Makefile
\end{lstlisting}
Then try again make c-all (make always sure that before 
typing make c-all that the deal.II path is exported - see above).
